Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-18 paper.qmd
Added 2D model overlaid on data (MNIST data)

pacmap_plot_mnist <- pacmap_minst_scaled |> 
  ggplot(aes(x = PaCMAP1, 
             y = PaCMAP2)) + 
  geom_point(alpha=0.1)

@@

::: {#fig-mnist1-sc layout-ncol="3" fig-pos="H"}
![](figures/mnist/sc_1.png){#fig-mnist1-sc1}

>>>>

pacmap_plot_mnist <- pacmap_minst_scaled |> 
  ggplot(aes(x = PaCMAP1, 
             y = PaCMAP2)) + 
  geom_point(alpha=0.1, color = "#6a3d9a")

@@

::: {#fig-mnist1-sc layout-ncol="4" fig-pos="H"}
![](figures/mnist/mnist_model_2d.png){#fig-mnist1-model}

![](figures/mnist/sc_1.png){#fig-mnist1-sc1}
